\documentclass[11pt]{ross}
\title{What to Bring?}

\newcommand{\spa}{\hspace*{1cm}}
\newcommand{\spz}{\hspace*{5mm}}

\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}

\begin{document}
\maketitle
 \begin{enumerate}[label=(\arabic*),itemsep=2em,topsep=-1em]

\item \textbf{What to bring?}
 \begin{enumerate}[label=(\alph*),itemsep=0.5em,topsep=0em]
 \item Bring clothes suitable for hot summer weather outside, and cool
   temperatures in air-conditioned buildings.  Bring (or plan to
   purchase) personal toiletries like soap, shampoo, deodorant,
   toothbrush and toothpaste, comb, brush, nail clippers, etc.
 \item Bring a pillow.  Clean sheets, pillowcase, and towel are
   provided weekly.  However, pillows are not distributed by the dorm
   staff.  You may bring your own pillow, or purchase a
   pillow after you arrive.
 \item A microwave oven and small refrigerator will be available in
   the dorm lobby.  Those appliances are not provided in student
   rooms.
 \item Washers and Dryers are available in the dorm at no charge.  The
   Ross Program will provide detergent for everyone to use.
 \item You are welcome to bring a phone, tablet, or laptop computer.
   You may certainly bring school supplies like paper, 
   pencils, pens, notebooks, and folders. There will also be opportunities 
   to purchase those items after you arrive.
\end{enumerate}
\item \textbf{What not to bring?}
  \begin{enumerate}[label=(\alph*),itemsep=0.5em,topsep=0em]
  \item Do not bring a gaming system, music player with speakers, 
    or other entertainment devices.  
    Counselors will confiscate such equipment if you bring it to the
    Ross Program.
  \item Student phones and computers are permitted, but their use is
    restricted: Make telephone calls only within your dorm room.
    Please do not use your phone or computer to play games, surf the internet, or
    look up information that undercuts the process of your
    mathematical explorations.
  \item Do not bring math books, number theory textbooks, or other references.  
    The Ross Number Theory course is self-contained, with no need for 
    outside texts.  It is far better to be puzzled by hard math problems 
    and discuss them with others, rather than searching for answers online.
  \item Do not bring skate boards, bicycles, or other transportation devices.
    Ross participants are asked stay on campus and walk to classes and cafeterias. 
  \item Do not bring valuable items or large amounts of cash.  The
    campus is a relatively safe place, with little crime.  But
    outsiders can sometimes sneak into the dormitory building and look
    for open doors when no one is there.
  \item Do not plan other activities while at the Ross Program. All of 
    your time, effort, and focus will be on the Ross courses and problem 
    sets.  There is no opportunity for you to take an on-line course, 
    prepare for the SAT, write essays for your upcoming English 
    class, or read the book recommended by your college advisor.
  \item There is free time for students to play outdoor games (soccer, Ultimate, 
    basketball, etc), or to play music on a University piano or your own 
    instrument. (But not in the dorm where others could be disturbed.)
   \item Please do not engage in activities like indoor gaming, card playing, 
    preparing for future tests, working on non-math classes, or reading books 
    unrelated to Ross courses. Those activities use up
    the intellectual energy that should be spent on Ross math problems!
\end{enumerate}
\end{enumerate}

\end{document}



