\documentclass[11pt]{rossasia}
\title{What to Bring?}

\newcommand{\spa}{\hspace*{1cm}}
\newcommand{\spz}{\hspace*{5mm}}

\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}

\begin{document}
\maketitle
 \begin{enumerate}[label=(\arabic*),itemsep=2em,topsep=-1em]
\item \textbf{What to bring?}
 \begin{enumerate}[label=(\alph*),itemsep=0.5em,topsep=0em]
 \item Bring clothing suitable for hot, humid summer weather outside, and for 
   cool \linebreak temperatures inside air-conditioned buildings.  
\item Bring (or plan to
   purchase) personal toiletries like soap, shampoo, deodorant,
   toothbrush, toothpaste, comb, brush, nail clippers, etc.
 \item  Each bed has a set of linens (sheets, pillow, etc).
   The dorm provides a clean set of sheets, pillowcase, and towel 
   every two weeks.  Of course, you may bring your own linens
   if desired.
 \item Washers and dryers are available in the dorm at no charge.  The
   Ross Program will provide detergent for everyone to use.
 \item Microwave ovens and small refrigerators are available in
   the dorm lobby.  
\item You may bring school supplies like paper, pencils, pens,
   notebooks.  But there will also be opportunities to purchase those
   items after you arrive.
\item   ATMs are available nearby. 
    You can usually withdraw cash (RMB) from a\linebreak 
     foreign bank account using a debit card.
    Non-Chinese credit cards are not widely accepted.
\end{enumerate}

\item \textbf{What not to bring?}
  \begin{enumerate}[label=(\alph*),itemsep=0.5em,topsep=0em]
  \item Do not bring electronic equipment like a computer, laptop,
    tablet, gaming system, music player with speakers, etc.  
    Counselors will confiscate such equipment, if you bring it to the
    Ross Program.
  \item Student cell phones are permitted, but their use is
    restricted. Phones must be turned off during classes, seminars,
    and mathematical discussions.  Make phone calls only within your dorm room.
    Please do not use your phone to play games or surf the internet.
    Looking up mathematical information will undercut the process of your
    mathematical explorations.
  \item Do not bring math books, number theory textbooks, or other references.  
    The Ross Number Theory course is self-contained, with no need for 
    outside texts.
  \item Do not bring valuable items, or large amounts of cash.  The
    campus is a relatively safe place, with little crime.  But
    outsiders can sometimes sneak into the dormitory building and look
    for open doors. There are no lockable closets or drawers inside the dorm rooms.

\end{enumerate}

\pagebreak
  \item {\bf Activities.} 
  
  Ross campers need to concentrate {\bf all} of their 
    intellectual efforts on the Ross courses and problem sets. 
    \begin{enumerate}[label=(\alph*),itemsep=0.5em,topsep=0em]
 \item   Do not plan to do other activities during the Ross Program. \\
    There is no opportunity for you to take an on-line course, 
    prepare  for the SAT, write essays for your upcoming English 
    class, or read the book recommended by your college advisor.
\item There is free time for students to play outdoor games. Ross participants
    have access to a running track, basketball course, and soccer field. \\
    Unfortunately, 
    no indoor spaces for sports are available.


\end{enumerate}
\end{enumerate}

\end{document}
