\documentclass{ross}
\title{Driving Directions}

\usepackage{hyperref}

\newcommand{\spa}{\hspace*{1cm}}

\begin{document}
\maketitle

Ohio Dominican University (ODU) is located at 1216 Sunbury Road, Columbus, OH 43219

The University's web page 
\href{https://www.ohiodominican.edu/future-students/admissions-aid/visit-odu/locations}{Visit ODU}  provides directions for driving to the ODU campus.  Near the bottom of that page, click on ``Directions.''   

When you get to the campus, drive to \dormname\ (our dorm, not to be
confused with the road which is ``Sunbury'') and park in the Gold Lot.
Use the parking pass that you have been sent.  There is a much smaller
lot north of the dorm, but the Gold Lot is easier parking.

Here are more precise directions:

\spa Sunbury Road runs north and south, passing through the ODU campus.\\
\spa There is one traffic light on Sunbury Road at ODU. \\
\spa \dormname\ is near traffic light, on the east side of Sunbury. \\
\spa The Gold Lot is to the west side of Sunbury.
 
{\bf Driving north} on Sunbury: The Gold Lot is the left turn at the traffic signal.

{\bf Driving south} on Sunbury: The Gold Lot is the right turn at the traffic signal.

When you arrive, call 1 (844) 262-8409 to talk to Jim Fowler.

A University staff person, or a Ross counselor, will meet you in front
of the \dormname\ to provide room keys and/or key-card.  You will then
perform a COVID--19 antigen test to self-administer.  If the test is
negative, then you can unload your belongings and settle into your
room. If you test positive, you'll be directed to quarantine housing.
See our ``COVID--19 Safety Protocols'' document from the HelloSign
participation agreement for more details.

There is a Ross Orientation meeting at 7pm on Tuesday June 14 in
\orientationlocation.


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
