\documentclass{ross}
\title{Driving Directions}

\hypersetup{hidelinks}

\newcommand{\spa}{\hspace*{1cm}}
\usepackage{parskip}

\begin{document}
\maketitle

Rose-Hulman Institute of Technology (RHIT) is located at:
\begin{center}
    5500 Wabash Ave, Terre Haute, IN 47803
\end{center}

The University's web page:
\begin{center}
    \href{https://www.rose-hulman.edu/visit/maps-and-directions/index.html}{\ttfamily\color{blue} https://www.rose-hulman.edu/visit/maps-and-directions/index.html}
\end{center}
provides directions for driving to the RHIT campus.  Near the bottom of that page, click the button ``{\sffamily GOOGLE MAP}.'' You may also find the following printable campus map at:
\begin{center}
    \href{https://www.rose-hulman.edu/visit/maps-and-directions/printable-map.html}{\ttfamily\color{blue}https://www.rose-hulman.edu/visit/maps-and-directions/printable-map.html} 
\end{center}
to be useful. 

When you get to the campus, drive to our dorm: Percopo Hall (building ``I'' by the lake on the \href{https://www.rose-hulman.edu/visit/maps-and-directions/printable-map.html}{\color{blue}campus map}). Park in front of the building in the ``Percopo Lot.''  

Here are more precise directions:

\begin{itemize}
\item The main driveway into Rose-Hulman campus is off of Wabash Ave (also known as US Highway 40). 
\item There is a traffic light on Wabash Ave to turn into Rose-Hulman campus. Approaching from the west, you'll turn left; approaching from the east, you'll turn right. 
\item After turning into Rose-Hulman campus from Wabash Ave, make the first left; Percopo Hall will be on your right-hand side a little ways down.
\end{itemize}

A University staff person, or a Ross counselor, will meet you in front of the dorm building to provide room keys and/or key-card.  You will then perform a COVID--19 antigen test.  If the test is negative, then you can unload your belongings and settle into your room. If you test positive, you'll be directed to quarantine housing. See our ``COVID--19 Safety Protocols'' document for more details.

Ross Orientation meeting:  7:00 PM on Sunday June 19 in Myers Hall 137.


\end{document}