\documentclass{ross}
\usepackage[T1]{fontenc}
\title{Employment Agreement}
\geometry{top=1.75in,bottom=1in}
\begin{document}
\maketitle

This Employment Agreement (the ``Agreement'') made as of \blank{1in}{date}{date} is
entered into by the Ross Mathematics Foundation (the ``Foundation'') \\
and \blank{2in}{Employee}{employee} (the ``Employee'').\\

The Ross Mathematics Foundation desires to employ the Employee, and
the Employee desires to be employed by the Foundation.  
In consideration of the premises and the mutual covenants
set forth herein and for other good and valuable consideration, the
receipt and sufficiency of which are hereby acknowledged, the parties
hereto covenant and agree as follows.

\section{Terms and duties}

\subsection{Term of employment}

The term of the Agreement shall commence at 12:01 \textsc{a.m.} on 
\blank{1in}{starting date}{startdate} and conclude at midnight on
\blank{1in}{ending date}{enddate}.

\subsection{Duties and responsibilities}

During the term of the Agreement, the Employee shall be a Counselor at
the Ross Mathematics Program.  The Employee is directly responsible
for the supervision of several students.  The Employee reads and
grades each of his/her assigned student's work on the daily sets of
math problems, discussing mathematical questions with those students,
and encouraging them to stay on task and concentrate on the problem
sets.  The Employee and other Ross Counselors share responsibility for dormitory life, setting the
tone, acting as role models, and supervising student behaviors.  The
Employee is encouraged to present his/her own mathematical lectures in
the dormitory to others who are interested.  At the
conclusion of the Program, the Employee shall
provide the Foundation with a full report, including a summary of the performance of
each of the students assigned to him/her.

\section{Compensation and benefits}

During the term of the Agreement, the Foundation shall pay to the
Employee a base salary (the ``Base Salary'') of \$3500 for the entire
period.  The Base Salary shall be paid in one installment consistent with
the Foundation's usual payroll practices.

\section{Termination}

This Agreement may be terminated by the Foundation for cause at any time upon written notice by the Foundation to the Employee.  Cause includes the Foundation's reasonable determination that the Employee is willfully failing to perform his/her duties or has engaged in wrongdoing which could be detrimental to the Foundation or to the safety of the participants in the Program.

Should the Employee's employment be terminated by the Foundation for cause, he/she shall not be entitled to any salary or benefit continuation beyond the date of termination, other than as required by applicable law or pursuant to any Foundation benefit plan or policy.

\section{Miscellaneous}

\subsection{Notices and Other Communications}

Any and all notices, requests, demands and other communications required or otherwise contemplated to be made under this Agreement shall be in writing and shall be provided by one or more of the following means and shall be deemed to have been duly given  if delivered personally, when received, or mailed by pre-paid registered or certified mail, return receipt requested, addressed as follows:

If to the Employee: \blank{3in}{Employee's address}{address}

If to the Foundation: 1644 Andover Rd, Columbus, Ohio, 43212.

\subsection{Successors and Assigns}

This Agreement shall be binding upon and inure to the benefit of the parties and their successors and assigns. Neither the Foundation nor the Employee shall assign this Agreement or any rights or obligations hereunder without the prior written consent of the other.

\subsection{Governing Law}

This Agreement shall be governed by the laws of the State of Ohio.

\subsection{Entire Agreement}

This Agreement constitutes the entire understanding of the parties with respect to the subject matter hereof and supersedes all prior agreements and understandings, oral or written, with respect to such matters.  Further this Agreement may not be amended except by a written amendment executed by both parties.

\subsection{Counterparts}

This agreement may be executed in any number of counterparts, each of which when executed and delivered shall constitute a duplicate original, but all counterparts together shall constitute a single agreement.

\textsc{In Witness Whereof} the parties have executed this Agreement as of the day and year set forth above.

\vspace{0.75in}
\hfill Signed \blank{3in}{Ross Mathematics Foundation}{foundation}

\vspace{0.5in}
\hfill  \blank{3in}{Employee}{employee}

   


\end{document}