\documentclass{ross}
\title{Standards of Behavior}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

\begin{document}
\maketitle
Expected behaviors for participants:
\begin{itemize}
\item Treat other people the way you would like to be treated.
\item Attend all scheduled online meetings for the Number Theory course.
\item Spend almost all of your time and effort working on Ross math classes and\\ problem sets.
\item Follow the rules set by the staff.
\end{itemize}

Behaviors that are not permitted:
\begin{itemize}
\item Using other people's work without attribution.
\item Lying or otherwise deceiving staff.
\item Spending time and attention on things unrelated to mathematics.
\item Fighting, harassing, cyber-bullying, or otherwise intimidating or demeaning others, such as by making comments which are derogatory with respect to color, disability, ethnicity, gender, race, religion, sexual orientation, or by making sexually suggestive, humiliating, or inappropriate comments to or about other people.
\item Behaving in a manner which is potentially dangerous to self and others.
\item Sharing photographs of participants without their permission.
\end{itemize}

Consequences of violations of the standards of behavior:
\begin{itemize}
\item Ross Program Counselors and Administrators will be made aware of
  the violation.
\item Parents/guardians will be notified.
\item The participant will be removed from the Program.
\item When warranted, the situation may be turned over to law
  enforcement authorities.
\end{itemize}

\vspace{0.5in}
\hfill Signed \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Parent or legal guardian signature} }

%\hfill Signed \blank{3in}{Parent or legal guardian}{parent}

\vspace{0.5in}

\hfill  \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Participant signature} }


%\hfill  \blank{3in}{Student}{student}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
