\documentclass{ross}
\title{Online Program Participation Agreement}

\begin{document}
\maketitle


On this \blank{1in}{date}{date}, I, \blank{3in}{parent/guardian name}{parent}, as parent or guardian, \\[5pt]
give permission for \blank{2in}{student name}{name} to attend the Ross Mathematics Program \\[5pt]
to be held online from \startsunday\today\
through \finishfriday\today.

\begin{description}
\item[Program Rules Agreement:] I, as student, understand and will
  abide by the rules and regulations of the Ross Mathematics Program,
  as listed in the ``Standards of Behavior.'' I, as parent or
  guardian, have read these documents and agree that the student will
  abide by them.
  
\item[Early Departure Agreement:] In the event that the Ross
  administrators determine that the student is gaining no academic
  benefits from the Program and/or acts in a manner that poses a
  threat to the safety and/or well-being of themselves or others and/or
  violates Program Rules, then I (as parent or guardian) agree that
  the student will leave the Ross Program immediately. \\
Program fees will not be refunded for early departures.\\
   For the
  duration of the Program, I can be reached at
  \blank{2in}{email}{email} and via telephone and text message at
  \blank{1.5in}{phone}{phone}. 
   I agree to respond to all messages within 24 hours. \\

  I, as student, agree to leave early if asked.  

\item[Liability Release:] I/we hereby release and forever discharge
  the Ross Mathematics Foundation, the Board of Trustees, and all
  employees and officers and agents and contractors of these entities
  from any and all claims, demands, or actions for personal injury,
  loss or theft of personal property, or any other damages which may
  arise out of or be in any way related to their conduct associated
  with the Ross Mathematics Program.
\item[Photo/Video Release:] I, as student, hereby grant the Ross
  Mathematics Foundation permission to use my likeness in
  photographs(s)/video in any and all of its publications and in any
  and all other media, whether now known or hereafter existing. I will
  make no monetary or other claim against the Ross Mathematics Foundation for the use of the photograph(s)/video. I, as parent or
  guardian, give the Ross Mathematics Foundation permission to publish in
  print, electronic, or video format the likeness or image of my
  child. I release all claims against the Program and the University
  with respect to copyright ownership and publication including any
  claim for compensation related to use of the materials.
\end{description}

\pagebreak

I, as parent or guardian, agree to be available during the entire six
week duration of the Ross Program to deal with emergencies and/or early
departures.

\vspace{0.5in}
\hfill Signed \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Parent or legal guardian signature} }

%\hfill Signed \blank{3in}{Parent or legal guardian}{parent}

\vspace{0.5in}

\hfill  \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Student signature} }


%\hfill  \blank{3in}{Student}{student}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
