\documentclass{ross}
\title{Privacy Policy}

\begin{document}
\maketitle

The Ross Mathematics Foundation (the ``Foundation'') takes privacy
seriously. This Policy explains how we collect, use, disclose, and
safeguard your personal information when you visit
\url{https://rossprogram.org/}, Circle Z, and other media outlets like
Facebook and Twitter that are related to the Ross Program.  We
collectively refers to these as the ``Site.''

\section{What information is collected?}

The Ross Foundation collects information about you in a variety of
ways. This includes personally identifiable information, such as your
name, home address, school address, email address, and telephone
number, and demographic information, such as your age and gender, that
you voluntarily give to us when you apply at
\url{https://apply.rossprogram.org/}.  You are under no obligation to
provide us with personal information of any kind.

Additionally, the Foundation records other information such as your IP
address, your browser, your local timezone, your access times when you
visit the Site.  Financial data, such as that related to your payment
method, is stored by our payment processor, Stripe.  You are directed
to Stripe's policy for more information on how Stripe protects your
financial data.  Homework submissions, feedback, and other messages
sent over Circle Z may be logged.  Finally, we may use cookies or
other web tracking technologies to track your use of the Site,
such as Google Analytics.  This information permits us to analyze
and track use of the Site.

\section{Security of your information}

We have taken reasonable steps to secure the information you provide
to us. For example, audio and text chats are encrypted between your
computer and the Foundation's servers.  However, no security measures
are perfect, and any information the Foundation collects could be
misused and consequently the Foundation cannot guarantee the security
of your information.

\section{Your options}

You may terminate your Ross account by contacting us using the contact
information provided below.  After we receive your request, we will
delete information about you that is stored in our databases.  Some
information may be retained in our files to prevent academic
misconduct, to troubleshoot technical problems with our platforms, and
to comply with legal requirements.  You may also opt-out of emails or
other communications from us.

If you are under 18 years of age or reside in California, you have the
right to request removal of data you posted on the Site. To request
removal of such data, please contact us using the contact information
provided below. When such a request is received, we will delete your forum posts.

\section{Contact us}

If you have questions or comments about this Privacy Policy, please
contact the Foundation by emailing \url{ross@rossprogram.org} or by
writing to 1644 Andover Rd, Columbus, Ohio, 43212.

\vspace{0.5in}
\hfill Signed \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Parent or legal guardian signature} }

%\hfill Signed \blank{3in}{Parent or legal guardian}{parent}

\vspace{0.5in}

\hfill  \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Student signature} }


%\hfill  \blank{3in}{Student}{student}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
