\documentclass{ross}
\title{Program Participation Agreement}

\begin{document}
\maketitle
For this Agreement, please type the requested information into the response spaces.
Print the document, add signatures of Parent (or legal guardian), and of Student.  
Then scan the signed document to create a PDF file, and email that file
to: \texttt{agreement@rossprogram.org} . \\

On this \blank{1in}{date}{date}, I, \blank{3in}{ parent/guardian name}{parent}, 
as parent or guardian, \\[5pt]
give permission for \blank{2in}{student name }{name} to attend the Ross Mathematics Program \\[5pt]
to be held at Ohio Dominican University from \startsunday\today\ through
\finishfriday\today.

\begin{description}
\item[Program Rules Agreement:] I, as student, understand and will
  abide by the rules and regulations of \campus\ as
  well as those of the Ross Mathematics Program, as listed in the
  ``Standards of Behavior.'' I, as parent or guardian, have read
  these documents and agree that the student will abide by them.
\item[Early Departure Agreement:] In the event that the Ross
  administrators determine that the student is gaining no academic
  benefits from the Program and/or acts in a manner that poses a
  threat to the safety and/or wellbeing of themselves or others and/or
  violates Program Rules, then I (as parent or guardian) agree that
  the student will leave the Ross Program immediately, will be
  returned to my custody, and I will assume responsibility for all
  travel costs and all costs for receiving the student. \\
  For the duration of the Program, I can be reached at
  \blank{2in}{email}{email} and via telephone and text message at
  \blank{1.5in}{phone}{phone}. \\[5pt]
   I agree to respond to all messages within 24 hours. \\[1ex]
I, as student, agree to leave early if asked.  \\
Program fees will not be returned for early departures.
\item[Cell phones and other networked devices:] In order to contact
his/her parents/guardian, each student is permitted to use a cell
phone and/or laptop computer. Ross students are not otherwise
permitted to use a cell phone or any other device containing a radio
transmitter or connection to the internet.  The Ross Mathematics
Foundation may require the use of certain applications or websites
which may collect location data to ensure participants do not leave
campus without approval.  The Ross Mathematics Foundation does not
sell, give, or trade the data we store to any third parties for
marketing purposes.
\item[Property Agreement:] I/we agree to cover the cost of any loss of
  or damage to any property for which the student is directly
  personally responsible.
\item[Lost key and key-card fees:] I, as parent or guardian, am
financially responsible for the cost of changing locks and producing
keys to residence hall doors if the student does not return his/her
keys at check out.  Replacements for key-cards are at least \$50
dollars; dorm room keys or bathroom keys are at least \$125 dollars to
replace.  Additional charges to re-key locks may be levied if needed.
\item[Health Insurance Agreement:] Prior to participation in the Ross
  Program, I/we agree to acquire and maintain a policy of health
  insurance covering hospitalization and medical treatment for any
  illnesses or injuries incurred during participation in the
  program. Such insurance shall be valid for the duration of the
  Program and be issued by an insurance company authorized to do
  business within the appropriate state in the USA.
\item[Liability Release:] I/we hereby release and forever discharge
  the the Ross Mathematics Foundation, 
  \campus, the Board  of Trustees, and 
  all employees and officers and agents of these entities from any
  and all claims, demands, or actions for personal injury, loss or
  theft of personal property, or any other damages which may arise out
  of or be in any way related to their conduct associated with the
  Ross Mathematics Program.
  \item[COVID-19:] Because \campus\ is open for use
by other individuals, I/we recognize that I am/we are at higher risk of 
contracting COVID-19. With full awareness and appreciation of
the risks involved, I, for myself and on behalf of my family, estate,
heirs, executors, administrators, assigns, and personal representatives, 
hereby forever release, waive, discharge, and covenant not to sue the 
Ross Mathematics Foundation, its board members, administrators, and 
employees (collectively the  ``Released Parties'') from any and all liability, 
claims, demands, actions, and causes of action whatsoever, directly or 
indirectly arising out of or related to any loss, damage, or injury, 
including death, that may be sustained by me related to COVID-19 whether
caused by the negligence of the Released Parties, any third-party using 
\campus\, or otherwise, while participating in any activity while in, on, 
or around \campus\ and/or while using any \campus\ facilities, tools, 
equipment, or materials. I/we agree to indemnify, defend, and hold 
harmless the Released Parties from and against any and all costs, expenses,
damages, claims, lawsuits, judgments, losses, and/or liabilities 
(including attorney fees) arising either directly or indirectly from or 
related to any and all claims made by or against any of the Released 
Parties due to bodily injury, death, loss of use, monetary loss, or 
any other injury from or related to my use of the \campus\ facilities,
tools, equipment, or materials, whether caused by the negligence of 
the Released Parties or otherwise specifically related to COVID-19.
\item[Photo/Video Release:] I, as student, hereby grant the Ross
  Mathematics Foundation permission to use my likeness in
  photographs(s)/video in any and all of its publications and in any
  and all other media, whether now known or hereafter existing. I will
  make no monetary or other claim against the Ross Mathematics Foundation or
 \campus\ for the use of the photographs(s)/video. I, as parent or
  guardian, give the Ross Mathematics Foundation permission to publish in
  print, electronic, or video format the likeness or image of my
  child. I release all claims against the Program and the University
  with respect to copyright ownership and publication including any
  claim for compensation related to use of the materials.
\item[Transportation Agreement:] I, as parent or guardian, do hereby
  grant Ross Mathematics Foundation administrators and counselors
  permission to transport my child by personal, commercial, and/or
  university vehicle, or by foot, to and from airports, all program
  activities on and off-campus, and/or in the event of a medical
  emergency.
\end{description}
I, as parent or guardian, agree to be available during the entire six
week duration of the Ross Program to deal with emergencies and/or early
departures.

\vspace{0.5in}
\hfill Signed \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Parent or legal guardian signature} }

%\hfill Signed \blank{3in}{Parent or legal guardian}{parent}

\vspace{0.5in}

\hfill  \rule{3in}{0.1mm}\\[-1.5mm]
\hspace*{3.7in} {\footnotesize \textcolor{gray}{Student signature} }


%\hfill  \blank{3in}{Student}{student}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
