\documentclass[11pt]{ross}
\title{Program Fees}

\usepackage{verbatim}  % to allow multi-line comments

\begin{document}
\maketitle

We must receive your program fee prior to \feeduedate.  You may pay
program fees by paper check, credit card, or electronic funds wire
transfer.

Program Fees are used to pay for room and board costs, and instructional expenses.
\begin{quote}
Total Fee is \totalfee \ (US dollars)
\end{quote}  

Participants must pay this program fee prior to \feeduedate.

\subsection*{To pay by Paper Check}

If you reside in the USA, you may write a check for \totalfee minus
the \$75 paper check discount, payable in U.S. Dollars, made out to
``Ross Mathematics Foundation'' and mailed to
\begin{quote}
Ross Mathematics Foundation  \\
1644 Andover Rd \\
Columbus, OH 43212
\end{quote} U.S. residents should allow time for postal delivery, or
use an express/certified mail delivery service. Do not require
signature confirmation because no one is available to sign for
packages.  Mail from other countries sometimes takes much longer.
Check with your local postmaster for a delivery time estimate.

\textbf{We are happy to receive paper checks} and offer a discount for
using a paper check.  However, if you live outside the USA it might be
more convenient to pay by another method.

\subsection*{To pay by Credit Card}

The Ross Mathematics Foundation can receive payments by credit card.
Visit \url{https://apply.rossprogram.org/} and click the ``Pay Course
Fees'' button to pay by credit card.

\subsection*{To pay by Electronic Funds Transfer}

If you live abroad and cannot pay by credit card or provide a paper
check, you may instead pay participation fees by emailing
\texttt{ross@rossproram.org} to arrange an electronic funds wire
transfer.

Your email must include your bank information, the name on the account
from which you are sending the funds, and the total amount of the wire
transfer in USD.  You are responsible for all wire transfer fees;
include sufficient funds to cover your bank's origination fee, any
currency conversion fees, and an additional \$15 to cover our bank's
incoming wire fee.  Furthermore, \textbf{be sure that the wire
  transfer instructions include the participant's full name} so that
we may credit your account.

\begin{tabular}{ll}
  \textbf{Bank Name:} &  HUNTINGTON NATIONAL BANK \\
&  International Services EA2E85, 7 Easton Oval \\
&  Columbus, OH 43219   \\
\textbf{Routing number:} &  044000024 \\
\textbf{Swift Code (International):} & HUNTUS33 \\
\textbf{Bank Account Name:} & ROSS MATHEMATICS FOUNDATION \\
\textbf{Account Number:} &  01893542541 \\
  \textbf{Instructions:} &  \textit{\textbf{Include the participant's name}} \\
\end{tabular}

We must receive your program fee prior to \feeduedate.
credit your account.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
