\documentclass{ross}

\usepackage{enumerate}
\usepackage{enumitem}

\title{Program Rules}
\begin{document}
\maketitle
Participants are {\bf not} allowed to bring the following items to the Ross
Program:
\begin{itemize}
\item Televisions, games or gaming systems, music players with speakers, or similar systems,
\item Valuable items or large amounts of cash (there are ATMs on campus),
\item Automobiles, bicycles, skateboards, etc.
\end{itemize}

\bigskip\hrule
\textbf{Cell Phones:} Students may bring cell phones, but there are restrictions. 
\begin{enumerate}[label=(\roman*),itemsep=0.5em,topsep= 0em]

\item {\it Classes.}  All phones must be off during classes or lectures. 

\item {\it Telephone and text.}  Do not make phone calls or send text messages 
where those actions might distract other people.

\item {\it Internet.} Avoid internet use during the Ross Program! 
It is tempting to read newsfeeds, play online games, watch videos, read (or write) blogs, 
find friends on Facebook, and surf through websites.  But such activities are huge time-wasters, 
and will distract you and your friends from concentrating on the challenging math problems we thrive on.  \\[5pt]
Working with math-oriented websites can {\it seem} productive. But if you're working on a 
hard Ross problem and then read related ideas online or in a book, you are under-cutting 
your own process of discovery. Work through the problems by your own efforts, and by having 
mathematial conversations with colleagues, JCs, and counselors.  Ross's central goal is to 
help you learn how to think like a mathematician.\\
\hspace*{1cm} Solutions are not as satisfying if you looked up the answers.

\item {\it Cameras.}  It is fine to take photos of friends in order to record and remember fun times.  
But some photos are not appropriate.  Be sure that anyone in a photo you take has given you permission 
for that picture.  This is especially important for any photos you send to others, or images that you post on social media. 

\item{\it Tracking.}  When you arrive on campus, a Ross staff member
may ask you to visit a certain Ross Program website and approve
location access.  Then the Ross administrators can find you in
emergencies. You may remove those permissions at the end of the six
weeks.
\end{enumerate}

\bigskip\hrule
\pagebreak

To help ensure basic safety, students are supervised 
by Ross Counselors at all times.

Ross participants may not leave the dormitory after dark unless 
in the company of a Counselor and going to a scheduled Ross activity.

\textbf{Do not leave the campus} unless absolutely necessary, and in
the company of a Counselor or other responsible adult.

We work hard to build an environment where students can focus on hard math problems
without distractions, maintain their mathematical momentum, 
and build a strong feeling of community within the dormitory. 
A trip away from the Ross community will decrease that momentum.

\underline{Off-campus Excursions}.  To leave campus with
an adult friend or family member, you must complete a {\it Leave Request Form} 
and have it approved by the Head Counselor prior to departure.

Standard rules regarding respect and behavior apply in the Ross
Program, just as they do in high schools. These basic rules of civil society hold 
for the duration of our summer program, both in and out of the classroom. 
Please review the Ross Program's \textit{Standards of Behavior} for
a clearer statement of what behaviors this involves.
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
