\documentclass{rossasia}
\title{Registration and Itinerary}

\newcommand{\spz}{\hspace*{5mm}}
\newcommand{\spa}{\hspace*{10mm}}


\begin{document}
\maketitle

{\bf Personal Information.}

Enter your full name (personal name followed by family name)\\[3pt]
\spa  \blank{9cm}{\hspace*{3em}first name \hspace*{4cm}last name}{name1} \

What do you want to be called by other people while at camp? \\[3pt]
\spa  \blank{6cm}{\hspace*{7em}nickname}{nickname} \

What email address and cell phone number will you use while at Ross/Asia this summer?\\[3pt]
\spa  \blank{9cm}{\hspace*{40mm}email}{email1} \\[8pt]
\spa  \blank{5cm}{\hspace*{15mm}phone number}{cell1} 

\bigskip\bigskip

Enter full name, email, and phone for your Emergency Contacts [typically, your parents]. \\
{\scriptsize (This information will be used if you have some illness or accident.) }

Contact \#1 \spz   \blank{9cm}{\hspace*{3em}first name \hspace*{37mm}last name}{name2} 

\spa  \blank{9cm}{\hspace*{42mm} email}{email2} \\[8pt]
\spa  \blank{5cm}{\hspace*{15mm}phone number}{cell21} \ \spa\spa  \blank{5cm}{\hspace*{15mm}phone number}{cell22} 

\bigskip

Contact \#2 \spz   \blank{9cm}{\hspace*{3em}first name \hspace*{37mm}last name}{name3} \

\spa   \blank{9cm}{\hspace*{42mm} email}{email3} \\[8pt]
\spa  \blank{5cm}{\hspace*{15mm}phone number}{cell31} \ \spa\spa  \blank{5cm}{\hspace*{15mm}phone number}{cell32} 

\vfill
{\scriptsize (continue to next page)}

\pagebreak

{\bf How will you arrive at the dormitory in Zhenjiang?}\\
Most participants will arrive in the afternoon on Sunday, 7 July 2019.  \\

\bigskip\hrule
{\bf By car:} 

When do you expect to arrive on campus?  \\[5pt]
\spa\spa \blank{5cm}{\hspace*{20mm}date}{date}  \hspace*{2cm} \blank{3cm}{\hspace*{10mm}time}{time}  


Type your information into the spaces above, save the completed document, and attach it to an email message sent to 
\texttt{ \href{mailto:info@rossmathasia.org}{info@rossmathasia.org}}. \\[3pt]

\bigskip\hrule
{\bf By plane or train:} 

Ross/Asia staff members will meet arriving campers in three locations, as described in the ``Travel Plan''  \url{https://rossprogram.org/arrival/asia/travel-plan.pdf}.:\\
\spa at the Shanghai/Pudong airport, \\
\spa at the Nanjing South Train Station, \\
\spa at our dormitory on the campus of the Jiangsu Aviation Technical College \\
\hspace*{15mm}at 88 Ruicheng Road, Zhengjiang.

Tell us which of those three options you plan to use.  \\
To do this, type your information into the spaces above, save the completed document, and attach it to an email message sent to 
\texttt{ \href{mailto:info@rossmathasia.org}{info@rossmathasia.org}}. \\[3pt]
In that message, also provide your full arrival itinerary, with the following information:  \\
\spz  \textbf{Where} (Shanghai, Nanjing, or Zhenjiang) $\;$ and $\;$   \textbf{When} (date and time) \\
you plan to meet the Ross/Asia staff.  Also include the details: \\
\spa  airlines, flight numbers, airports, and arrival times for your flights{\bf ;} \ and\\
\spa  train numbers, stations, and arrival times for your train travels.

\bigskip\bigskip

Information you send us will help Ross/Asia staff members be there when you arrive.

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
