\documentclass{ross}
\title{Standards of Behavior}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

\begin{document}
\maketitle

The goal of the Ross Mathematics Foundation is to create a wonderful
mathematical summer for all participants.  A summer of deep
mathematical focus and inquiry-based explorations requires us to work
together.  Be prepared to take an active, patient, and generous role
in your own learning and that of the other participants.

The Ross Mathematics Foundation will not tolerate discrimination,
harassment, or bullying.  Every participant has something to add to
our summer of mathematics.  The Foundation seeks to offer fair and
equitable treatment to every participant, and the Foundation will not
discriminate based on gender identity, nationality, race or ethnicity,
religion, age, marital status, sexual orientation, or disability.

Language you find acceptable may be offensive to others, so we aim for
a higher standard of care and concern to communicate our respect for
one another.  If you feel uncomfortable with the way that you are being
treated, or if you notice that someone else is being treated less than
excellently, please contact \texttt{ross@rossprogram.org} immediately.
You may alternatively submit an anonymous report or communicate with
the participant ombudsperson.

Expected behaviors for participants:
\begin{itemize}
\item Treat other people the way you would like to be treated.
\item Attend all classes for the Number Theory course.
\item Spend almost all of your time and effort working on mathematics.
\item Follow the rules set by the Counselors. (Counselors are in charge of dormitory life.)
\end{itemize}

Behaviors that are not permitted:
\begin{itemize}
\item Using other people's work without attribution.
\item Spending time and attention on things unrelated to math.
\item Leaving campus.\footnote{\label{counselors}Unless given explicit permission, and accompanied by a Ross Counselor or Administrator.}
\item Leaving the dormitory building after dark.\footnoteref{counselors}
\item Damaging property that belongs to others.
\item Taking photographs without the explicit permission of those being photographed.
\item Consuming alcohol, tobacco products, or illegal drugs.
\end{itemize}

\pagebreak

Consequences of violations of the standards of behavior:
\begin{itemize}
\item Ross Program Counselors and Administrators will be made aware of
  the violation.
\item Parents/guardians will be notified. If necessary, arrangements
  will be made to remove the participant from the program.
\item When warranted, the situation may be turned over to law
  enforcement authorities.
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
