\documentclass{rossasia}
\title{Standards of Behavior}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

\begin{document}
\maketitle
Expected behaviors for participants:
\begin{itemize}
\item Treat other people the way you would like to be treated.
\item Attend all classes (lectures and seminars) for the Number Theory course.
\item Spend almost all of your time and effort working on Ross math classes and \\
problem sets.
\item Follow the rules set by the Counselors. (Counselors are in charge of dormitory life.)
\end{itemize}

Behaviors that are not permitted:
\begin{itemize}
\item Using other people's work without attribution.
\item Bringing an electronic device with internet capability, other than a cell phone.\\
Using a cell phone for entertainment or for internet activities.
\item Spending time and attention on things unrelated to math.
\item Leaving campus.\footnote{\label{counselors}Unless given explicit permission, 
and accompanied by a Ross Counselor or other responsible adult.}
\item Leaving the dormitory building after dark.\footnoteref{counselors}
\item Damaging property that belongs to others.
\item Taking photographs without the explicit permission of those being photographed.
\item Consuming alcohol, tobacco products, or illegal drugs.
\end{itemize}

Consequences of violations of the standards of behavior:
\begin{itemize}
\item Ross Program Counselors and Administrators will be made aware of
  the violation.
\item Parents/guardians will be notified. If necessary, arrangements
  will be made to remove the participant from the program.
\item When warranted, the situation may be turned over to law
  enforcement authorities.
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
